\documentclass[11pt,letter]{article}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{CV}
\usepackage{changepage} %adjust page width
\usepackage{titlesec} % change
\usepackage[letterpaper]{geometry}
\geometry{top=1.25in, bottom=1.25in, left=1.0in, right=1.0in}
\def\baselinestretch{1.05}
\setlength{\parindent}{1cm}
\titlespacing*{\section}
{0pt}{1.5ex plus 1ex minus .2ex}{1.5ex plus .2ex}
\titlespacing*{\subsection}
{0pt}{1.5ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\begin{document}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setcounter{page}{1}
\pagestyle{fancyplain}
\fancyhf{}
\lfoot{\small\sl{Curriculum Vitae -- Qi~Zhang}}
%\rfoot{\thepage}
\rfoot{\thepage\ of \pageref{LastPage}}
%
\newcommand{\QZ}{\textbf{Q. Zhang}}
\newcommand{\DJB}{D. Bodony}
\newcommand{\UIUC}{University of Illinois at Urbana-Champaign}
%
% name%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
{\LARGE\textsc{QI ZHANG}}
\end{center}


\section*{Personal Information}
  \begin{minipage}{3.65in}
    \begin{tabular}{l}
   % \begin{flushleft}
  Address: 104 S Wright St.  Rm 326, Urbana, IL, 61801 \\
  Email: qizhang1@illinois.edu / bl1008@gmail.com\\
  Cell: (716)\,238-1959
%\end{flushleft}
    \end{tabular}
  \end{minipage}
  \begin{minipage}{3.65in}
    \begin{tabular}{r}
%\begin{flushright}
  Postdoc Research Associate\\
  Department of Aerospace Engineering\\
  University of Illinois Urbana-Champaign\\
  %326 Talbot Lab, 104 S Wright St, Urbana, IL, 61801
%\end{flushright}
    \end{tabular}
  \end{minipage}
  

\section*{Research Interests}
\begin{adjustwidth}{2em}{0pt}
Fluid Mechanics, Aeroacoustics, Computational Fluid Dynamics, Numerical Methods, \\ Large-scale Simulations, Turbulence, Partial Differential Equations
\end{adjustwidth}

%education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\section*{\sc{Education}}
%\vspace*{-3mm}
\begin{CV}
\item[2010 -- 2014]\textbf{Ph.D.} {Aerospace Engineering, University of Illinois at Urbana-Champaign}  \\%\hfill\textbf{GPA: 4.00} \\
Thesis: \emph{Direct Numerical Simulation and Analytical Modeling of 3-D Honeycomb Acoustic Liners. } \\
Advisor: \emph{Daniel J. Bodony}
\item[2008 -- 2009]\textbf{M.S.} {Aerospace Engineering, University of Illinois at Urbana-Champaign}\\%\hfill \textbf{GPA: 3.97} \\
Thesis: \emph{Numerical Simulation of 2-D Acoustic Liners with High Speed Grazing Flow.}  \\
Advisor: \emph{Daniel J. Bodony}
\item[2003 -- 2007]\textbf{B.S.}  {Theoretical and Applied Mechanics,   Fudan University, China}\\% \hfill \textbf{GPA: 3.53}
\end{CV} 


\section*{Academic Employment}
\begin{CV}
\item[2014 -- now] \textbf{Postdoc Research Associate}, \UIUC 
\item[2008 -- 2014] \textbf{Graduate Research Assistant}, \UIUC 
\item[2013] \textbf{Graduate Teaching Assistant}, \UIUC
\end{CV} 
%%
\section*{\sc{Publications}}
%\vspace*{-3mm}
\subsection*{\textbf{\underline{Journal Papers}}}
\begin{adjustwidth}{1em}{0pt}
\begin{enumerate}
\item \QZ\ and \DJB,  ``Numerical Investigation of 3-D Honeycomb Liner with Turbulent Boundary Layer. Part 1. Sound-orifice-boundary layer Interaction.'', Under consideration for publication in \emph{Journal of Fluid Mechanics}.
\item \QZ\ and \DJB,  ``Numerical Investigation of 3-D Honeycomb Liner with Turbulent Boundary Layer. Part 2. Impedance Prediction and Modeling.'', Under consideration for publication in \emph{Journal of Fluid Mechanics}.
\item \QZ\ and \DJB, (2012) ``Numerical Investigation and Modeling of Acoustically Excited Flow through a Circular Orifice Backed by a Hexagonal Cavity'', \emph{Journal of Fluid Mechanics}, Vol. 693, pp.367-401.
\item \QZ\  and \DJB, (2011) ``Numerical Simulation of Two-dimensional Acoustic Liners with High Speed Grazing Flow'', \emph{AIAA Journal}, Vol. 49(2), pp.365-382.
\item \DJB, G Zagaris, A Reichert, and  \QZ, (2010) ``Provably stable overset grid methods for computational aeroacoustics'', \emph{Journal of Sound and Vibration}, Vol. 330(17), pp.4161-4179.
\end{enumerate}
\end{adjustwidth}
\subsection*{\textbf{\underline{Conference Papers}}}
\begin{enumerate}
\item \QZ\ and \DJB,  (2014) {``Direct Numerical Simulation and Analytical Modeling of Locally Reacting, Single Degree of Freedom Acoustic Liners with Turbulent Grazing Flow''}, AIAA 2014-3354, \emph{20\textsuperscript{th}  AIAA/CEAS Aeroacoustics Conference}, Atlanta, GA.
\item \QZ\ and \DJB,  (2013) {``Impedance Prediction of Three-Dimensional Honeycomb Liners with Laminar/Turbulent Boundary Layers using DNS''}, AIAA 2012-0871, \emph{19\textsuperscript{th}  AIAA/CEAS Aeroacoustics Conference}, Berlin, Germany.
\item \QZ\ and \DJB,  (2012) {``Direct Numerical Simulation of Three-Dimensional Honeycomb Liners with Turbulent Boundary Layer''}, AIAA 2012-0871, \emph{18\textsuperscript{th}  AIAA/CEAS Aeroacoustics Conference}, Colorado Springs, CO.
\item \QZ\ and \DJB,  (2011) {``Impedance Predictions of 3D Honeycomb Liner with Circular Apertures by DNS''}, AIAA 2011-2727,   \emph{17\textsuperscript{th} AIAA/CEAS Aeroacoustics Conference}, Portland, OR.
\item \QZ\ and  \DJB,  (2011) {``Direct Numerical Simulation of Three Dimensional Hexagonal Acoustic Liners with Circular Apertures''}, AIAA 2011-0843, \emph{49\textsuperscript{th}  AIAA Aerospace Sciences Meeting}, Orlando, FL.
\item \DJB, G Zagaris, A Reichert, and  \QZ, (2010) {``Aeroacoustic predictions in complex geometries''}, Procedia Engineering, Vol. 6, pp. 234-243, \emph{IUTAM Symposium on Computational Aero-Acoustics for Aircraft Noise Prediction}, Southampton, United Kingdom.
\end{enumerate}

%\subsection*{Book Chapters}
%\begin{adjustwidth}{1em}{0pt}
%\begin{enumerate}
%\item  T.N. Wong, \textbf{C. Wang}, Y. Gao, N.T. Nguyen, C. Yang, and K.T. Ooi,
%``Liquid-liquid stratified flow in microchannels",
%in \emph{Encyclopedia of Microfluidics and Nanofluidics}, Springer, 2008.
%\end{enumerate}
%\end{adjustwidth}


%\section*{\sc\underline{Patents and Inventions}}%%%%%%%%%%%%%%%%%%%
%\begin{adjustwidth}{1em}{0pt}
%\begin{enumerate}
%\item   N.T. Nguyen, T.N. Wong, J.C. Chai, \textbf{C. Wang}, Y.F. Yap, and T.H. Ting,
%``Active control for droplet-based microfluidics", \emph{United States Patent Application} 20090181864, 2009.
%\item   T.N. Wong, N.T. Nguyen, C. Yang, J.C. Chai, and K.T. Ooi, \textbf{C. Wang} and Y. Gao.,
%    ``Method and apparatus for controlling multi-fluid flow in a micro channel", \emph{United States Patent} 7534097, 2009.
%\end{enumerate}
%\end{adjustwidth}
%
%\section*{\sc\underline{Invited Talks}}%%%%%%%%%%%%%%%%%%
%\begin{adjustwidth}{1em}{0pt}
%\begin{enumerate}
%
%\item ``Microscale transport phenomena: particle manipulation and liquid mixing with microbubble streaming flows", Civil and Mechanical Engineering Department, \textbf{University of Missouri at Kansas City}, Kansas City, MO, March 13, 2013.
%
%\item ``Microscale transport phenomena: particle manipulation and mixing with microbubble streaming flows", Department of Mechanical and Aerospace Engineering, \textbf{\MST}, Rolla, MO, February 14, 2013.
%
%\end{enumerate}
%\end{adjustwidth}
\section*{\sc{Contributed Talks and Conference Proceedings}}%%%%%%%%%%%%%%%%%%%%%%%%

\begin{adjustwidth}{1em}{0pt}
($\dag$ denotes presenter)
\begin{enumerate}
\item \QZ$\dag$, \DJB, ``{Numerical simulation and reduced-order modeling of the sound induced flow through a cavity-backed circular under turbulent boundary layer}",  \emph{67\textsuperscript{th} American Physical Society Division of Fluid Dynamics (APS DFD) Annual Meeting}, San Francisco, California, November 23-25, 2014.
\item \QZ$\dag$, \DJB, ``{Interaction of a turbulent boundary layer with a cavity-backed circular orifice and tonal acoustic excitation}",  \emph{66\textsuperscript{th} American Physical Society Division of Fluid Dynamics (APS DFD) Annual Meeting}, Pittsburgh, Pennsylvania, November 24-26, 2013.
\item \QZ$\dag$, \DJB, ``{Direct Numerical Simulations of Turbulent Boundary Layers Over A Circular Aperture}",  \emph{65\textsuperscript{th} American Physical Society Division of Fluid
Dynamics (APS DFD) Annual Meeting}, San Diego, California, November 18-20, 2012.
\item \QZ$\dag$, \DJB, ``{Near field of a transient, acoustically forced transitional and turbulent jet''}, \emph{64\textsuperscript{th} American Physical Society Division of Fluid
Dynamics (APS DFD) Annual Meeting}, Baltimore, Maryland, November 20-22, 2011.
\item \QZ$\dag$, \DJB, {``Direct Numerical Simulation of Three Dimensional Honeycomb Liner with Circular Apertures''}, \emph{63\textsuperscript{rd} American Physical Society Division of Fluid
Dynamics (APS DFD) Annual Meeting}, Long Beach, California, November 21-23, 2010.
\end{enumerate}
\end{adjustwidth}

\section*{\sc{Professional Memberships}}
\begin{adjustwidth}{2em}{0pt}
Member of American Physical Society (APS)\\ %\hfill 2009 -- present\\
Member of American Institute of Aeronautics and Astronautics (AIAA) %\hfill 2011 -- present
\end{adjustwidth}

\section*{\sc{Honors and Awards}}
\begin{adjustwidth}{5.5em}{0pt}
\begin{itemize}
%\item [2009] AIAA student conference (Region III, Midwest)  3\textsuperscript{rd} Prize.  
\item [2006 -- 2007] People's Fellowship of Fudan University, 1\textsuperscript{st} Prize
\item [2004 -- 2006] People's Fellowship of Fudan University, 2\textsuperscript{nd} Prize
\end{itemize}
\end{adjustwidth}

\section*{\sc{Peer Reviews}}%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{2em}{0pt}
%Biomicrofluidics\\
%Biomedical Microdevices\\
Journal of Computational and Nonlinear Dynamics\\
Journal of Theoretical and Computational Fluid Dynamics\\
Journal of Fluids Engineering\\
Journal of Turbulence
\end{adjustwidth}


% ######################Skills
\section*{\sc {Technical Expertise}}
\begin{itemize}
  \item \textbf{Programming Languages}: C/C++, Fortran,  Java, MATLAB, Mathematica,   Python, Unix Shell Scripting
  \item \textbf{Engineering Softwares}: Fluent, Tecplot, ANSYS, Gambit, Gridgen, Auto CAD 
%  \item \textbf{Operating Systems}: Linux, OSX, Microsoft Windows
\end{itemize}

\end{document} 